Live Functional Programming with Typed Holes

### 2018-04-30 discussion.tex
add to acks

The authors would like to thank Brigitte Pientka, Jonathan Aldrich, Joshua Sunshine, Michael Hilton, Claire LeGoues, the participants of the PL reading group at UChicago, and the referees and participants of the LIVE 2017 and Off the Beaten Track (OBT) 2017 workshops for their insights and feedback on various iterations of this work.

>>>>

The authors would like to thank Brigitte Pientka, Jonathan Aldrich, Joshua Sunshine, Michael Hilton, Claire LeGoues,
the participants of the PL reading group at UChicago,
and the referees and participants of the LIVE 2017 and Off the Beaten Track (OBT)
2017 workshops for their insights and feedback on various iterations of this work.
%
%%%%%%% BEGIN: Matt's Acks
%
This material is based in part upon work supported by a gift from
Facebook, and support from the National Science Foundation under grant
number CCF-1619282.
%
Any opinions, findings, and conclusions or recommendations expressed
in this material are those of the author(s) and do not necessarily
reflect the views of Mozilla, Facebook or the National Science Foundation.
%
%%%%%%% END: Matt's Acks
